An Online Visual Loop Closure Detection Method for Indoor Robotic Navigation

### 2014-12-01 latex-spie/article.tex
Eperiments is finished

The locations are represented with the histograms of their images. Detecting loop closing events can be considered as a machine learning problem which number of classes expands continuously when a new unseen location comes. We utilized Nearest Neighbour (NN) algorithm to classify locations by which the distance metric is the regular $L_1$ aka. Manhattan distance that is one of the simplest distance metric available. In other words, the image which distance between the input image is minimum closes the loop, if the distance is lower than the predefined threshold value.

@@

\section{METHODOLOGY}

@@

The method implemented in this paper has been evaluated on three datasets which lighting conditions are different from each other.

tested with k = 5, n = 2 ZM parameters
k x k is the number of regions the input image is divided
n: the order of ZM
tested in three different datasets by using image only, depth only and both image and depth.
image and depth is created by concatenated with image and depth ZM feature vectors

@@

        %%% BRIGHT DISTANCE MATRIX
        \begin{subfigure}[b]{0.27\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/dataset_bright.png}    
        \caption{Bright}
        \label{subfig:dataset_bright}
        \end{subfigure}
        ~ 
        %%% DIM DISTANCE MATRIX
        \begin{subfigure}[b]{0.27\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/dataset_dim.png}    
        \caption{Dim}
        \label{subfig:dataset_dim}
        \end{subfigure}
         ~ 
        %%% DARK DISTANCE MATRIX
        \begin{subfigure}[b]{0.27\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/dataset_dark.png}    
        \caption{Dark}
        \label{subfig:dataset_dark}
        \end{subfigure}

        \hspace{-5mm}
        \caption{Examplary images belonging to benchmark datasets in different lighting conditions.}
        \label{fig:dataset}
\end{figure}

@@

%%% BRIGHT PR CURVE
\begin{figure}[!htb]
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, height=8cm]{figures/pr_bright.eps}    
        \caption{Bright dataset results}
        \label{fig:pr_bright}
\end{figure}

%%% DIM PR CURVE
\begin{figure}[!htb]
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, height=8cm]{figures/pr_dim.eps}    
        \caption{Dim dataset results}
        \label{fig:pr_dim}
\end{figure}

%%% DARK PR CURVE
\begin{figure}[!htb]
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, height=8cm]{figures/pr_dark.eps}      
        \caption{Dark dataset results}
        \label{fig:pr_dark}
\end{figure}

>>>>

The locations are represented with the histograms of their images. Detecting loop closing events can be considered as a machine learning problem which number of classes expands continuously when a new unseen location comes. We utilized Nearest Neighbour (NN) algorithm to classify locations by which the distance metric is the regular $L_1$ a.k.a. Manhattan distance that is one of the simplest distance metric available. In other words, the image which distance between the input image is minimum closes the loop, if the distance is lower than the predefined threshold value.

@@

\section{METHODOLOGY}
\label{sec:method}

@@

The method implemented in this paper has been evaluated on three datasets which lighting conditions are different from each other. The tests are done with either using gray and depth images separately or using both of them. After that, the difference matrices are calculated to examine the results. Nearest Neighbour (NN) algorithm is utilized to classify the new locations and the distance metric is $L_{1}$.

The method described in Section \ref{sec:method} has basically two parameters that must be adjusted. One of them is $k\times k$ the size of subimages that the input image partitioned by in (\ref{eq:divided_mat}) and the other one is $n$ the order of the Zernike polynomials. During the experiments, the parameter set is selected as $k=30$ and $n=2$. Then the quantized $k\times k$-sized matrix obtained from the input image is divided into $5\times 5$ equal-sized non-overlapping subregions. The histograms of each subregion are simply concatenated to compose the feature vector of an image. In order to construct the ultimate feature vector containing both gray and depth images, each feature vectors obtained from both images are also concatenated.

@@

% BENCHMARK DATASETS
\begin{figure}[!htb]
        \centering

        %%% BRIGHT 
        \begin{subfigure}[b]{0.27\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/dataset_bright.png}    
        \caption{Bright}
        \label{subfig:dataset_bright}
        \end{subfigure}
        ~ 
        %%% DIM 
        \begin{subfigure}[b]{0.27\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/dataset_dim.png}    
        \caption{Dim}
        \label{subfig:dataset_dim}
        \end{subfigure}
         ~ 
        %%% DARK
        \begin{subfigure}[b]{0.27\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/dataset_dark.png}    
        \caption{Dark}
        \label{subfig:dataset_dark}
        \end{subfigure}

        \hspace{-3mm}
        \caption{Examplary images belonging to benchmark datasets in different lighting conditions.}
        \label{fig:dataset}
\end{figure}

@@

% RESULTS
\begin{figure}[!htb]
        \centering

        %%% BRIGHT PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_bright.eps}    
        \caption{Bright dataset results.}
        \label{subfig:pr_bright}
        \end{subfigure}
        ~ 
        %%% DIM PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dim.eps}    
        \caption{Dim dataset results.}
        \label{subfig:pr_dim}
        \end{subfigure}
        ~
        %%% DARK PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dark.eps}    
        \caption{Dark dataset results.}
        \label{subfig:pr_bright}
        \end{subfigure}
        ~ 
        %%% ALL PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_all.eps}    
        \caption{Comparison between datasets.}
        \label{subfig:pr_dim}
        \end{subfigure}

        \hspace{-3mm}
        \caption{PR curves}
        \label{fig:pr_curves}
\end{figure}
